Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-04 paper/main.tex
fix @RequestMapping("/awselb")

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx} 
\usepackage{textcomp}
\usepackage{xcolor}
\bibliographystyle{IEEEtran}
\usepackage[backend=biber,doi=true, natbib=true ]{biblatex}
\addbibresource{main.bib}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\subsection{Open Nighttime Lights}
this is the explaination  \cite{BARA2020106658}

@@

\subsection{ansible}
this is the explanation

\subsection{CloudFormation}
this is the explanation

\subsection{nginx/tomcat}
this is the explanation

@@

\printbibliography

>>>>

\usepackage[T1]{fontenc} 
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx} 
\usepackage{textcomp}
\usepackage{xcolor} 
% \bibliographystyle{IEEEtran} 
% \usepackage[backend=biber,doi=true, natbib=true ]{biblatex}
% \addbibresource{main.bib}

 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

@@

\subsection{Open Nighttime Lights}
% this is the explaination  \cite{BARA2020106658}

@@

\subsection{ansible}
Ansible is a famous open source deployment platform. Most of services in AWS can be working rightly with Ansible. We used it for our main sctructure deployment.

\subsection{CloudFormation}
CloudFormation is a service in AWS, which can organize our service very quickly and no codes need to write. The configuration in CloudFormation is a template which is just a yaml file. It is more convient than Ansible for some services. We use it deploy the RDS and Lambda Service.

\subsection{nginx/tomcat}
Nginx

@@

% \printbibliography
